Community-Conditioned Language Models

### 2020-11-02 paper/paper.tex
tweaks and notes
notes

At the the core of the community-conditioned language model (CCLM) 
is a standard $n$-layer neural sequence encoder 
with token embedding (we experiment with LSTM and transformer encoders).
To condition the model, we additionally train a \emph{community embedding},
which is concatenated with the hidden layer of the sequence encoder
for some layer $c \leq n$ and passed through a linear layer, 
which projects the resulting vector back down to the origial hidden size.
For $c = n$, the output of this linear layer is passed directly to the softmax function,
just as the final hidden layer of the sequence encoder is in other models.
For $c=0$, the community embedding is concatenated with the token embedding.
For this reason, we set the hidden size of the sequence encoder 
and the size of the token to be embedding equal for all models.

@@

We combined the 46 community corpora and split the combined corpus\jp{unclear if there is balancing between },
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.

We used a vocabulary size of \num{40000} tokens, with a special out-of-vocabulary token.
The vocabulary consisted of the most frequent tokens at the comment level,
meaning that we only counted each token once per comment.
The main reason for this was to avoid over-counting otherwise rare tokens that were spammed
many times in a single comment.

We trained the models on a simple left-to-right language modeling task 
with cross entropy loss over the vocabulary 
and AdamW \citep{Loshchilov2019} optimization, with an inital learning rate of \num{0.001}.
We used a batch size of \num{256} and a maximum sequence length of \num{64} tokens.
During training, a dropout rate of $0.1$ was applied between encoder layers 
and after each linear layer.

@@

We trained the models until the validation loss was smaller than the smallest
validation loss for two epochs in a row. 
The weights from the epoch with the smallest validation loss were used for testing.

@@

Knowing that $m$ \emph{actually} comes from community $c_j$, we can
measure the the precision our classifier, as a confusion matrix $C$,
which can be calculated as follows for a given set of posts:(TODO: what set exactly?)
\[C_{ij} = average_{m ∈ Posts(c_j)}(P(c=c_i | m))\].

>>>>

At the the core of the community-conditioned language model (CCLM) 
is a standard $n$\jp{with n=3}-layer neural sequence encoder
with token embedding (we experiment with LSTM and transformer encoders).
To condition the model, we additionally train a \emph{community embedding} parameter.
This parameter is concatenated with the hidden layer of the sequence encoder
for some layer $c \leq n$ and passed through a linear layer, 
which projects the resulting vector back down to the origial hidden size.
For $c = n$, the output of this linear layer is passed directly to the softmax function,
just as the final hidden layer of the sequence encoder is in other models.
For $c=0$, the community embedding is concatenated with the token embedding.
For this reason, we set the hidden size of the sequence encoder 
and the size of the token to be embedding equal for all models.

@@

We combined the 46 community corpora and split the combined corpus,
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.\jp{is it the same for testing/validation? How can you maintain this split?}

We used\jp{past tense is a bit awkward?} a vocabulary size of \num{40000} tokens, including a special out-of-vocabulary token.
The vocabulary consisted of the most frequent tokens at the comment level,
meaning that we only counted each token once per comment.
The main reason for this choice was to avoid over-counting otherwise rare tokens that were spammed
many times in a single comment.

We trained the models on a simple left-to-right\jp{I don't think that this applies for the transformer model} language modeling task 
with cross entropy loss over the vocabulary 
and AdamW \citep{Loshchilov2019} optimization, with an inital learning rate of \num{0.001}.
We used a batch size of \num{256} and a maximum sequence length of \num{64} tokens.\jp{What happens with longer sequences? Are sequences split at sentence boundaries?}
During training, a dropout rate of $0.1$ was applied between encoder layers 
and after each linear layer.

@@

We trained the models until the validation loss stopped decreasing for two epochs in a row.
\jp{How many epochs does that turn out to be? Is there a meaningful difference between lstm/}
The weights from the epoch with the smallest validation loss were used for testing.

@@

Knowing that $m$ \emph{actually} comes from community $c_j$, we can
measure the the precision our classifier, as a confusion matrix $C$,
which can be calculated as follows for a given set of posts:(TODO: what set exactly?)
\[C_{ij} = average_{\{m ∈ Posts(c_j)\}}(P(c=c_i | m))\].
